Paper Figures

### 2019-09-17 PaperFigures.Rmd
change the way p-values display

baseplot<-function(data, xval, yval, colors){
    ggplot(data, aes(data[,xval], data[,yval], fill=SM))+
    geom_boxplot(size=1, position=position_dodge(width = 1), outlier.shape = NA)+
    scale_fill_manual(values = colors)+
    theme_classic()+ theme(legend.position="none")+
    theme(panel.border = element_rect(fill = NA, colour = "black"))+
    theme(text = element_text(size=16))+
    theme(plot.title = element_text(hjust = 0.5)) +
    labs(x="", y="")
}

booleanplot<-function(data, xval, yval, colors){
    ggplot(data, aes(data[,xval], data[,yval], fill=SM))+
    geom_boxplot(size=1, position=position_dodge(width = 1), outlier.shape = NA)+
    scale_fill_manual(values = colors)+
    theme_classic()+ 
    theme(legend.position="none")+
    theme(text = element_text(size=16), axis.text.x = element_text(size=16))+
    theme(plot.title = element_text(hjust = 0.5)) +
    stat_compare_means(method="wilcox.test", label="p.signif", hide.ns = TRUE, size=10)+
    labs(x="", y="")
}

allplot<-function(data, xval, yval, colors){
    ggplot(data, aes(data[,xval], data[,yval], fill=disease))+
    geom_boxplot(size=1, position=position_dodge2(width=0.2, padding = 0.2, preserve = "single"), outlier.shape = NA)+
    scale_fill_manual(values = colors)+
    theme_classic()+ 
    theme(legend.position="none") +
    theme(panel.border = element_rect(fill = NA, colour = "black"))+
    facet_wrap(~variable)+
    scale_x_discrete(labels=c("SM- SM+\nHC", "SM- SM+\nLTBI", "SM- SM+\nTB"))+
    theme(text = element_text(size=16))+
    theme(plot.title = element_text(hjust = 0.5))+
    stat_compare_means(method = 'wilcox.test', label="p.signif", hide.ns=TRUE, size=10)+
    labs(x="", y="")
}

@@

tf<-allplot(melt, "TB", "value", all.cols)+    
    labs(y="(%) Total CD4+ T cells")

@@

sm<-allplot(melt, "TB", "value", all.cols) +    
    labs(y="(%) Total CD4+ T cells")

@@

@@

one<-allplot(melt, "TB", "value", all.cols)+ 
    facet_wrap(~variable, labeller = cyt_groups)+
    labs(y="(%) Total CD4+ T cells")

@@

two<-allplot(melt, "TB", "value", all.cols)+
    facet_wrap(~variable, labeller = cyt_groups)+
    coord_cartesian(ylim=c(0,8))+
    labs(y="(%) Total CD4+ T cells")

@@

cyt<-filter_hc(melt)
a<-baseplot(cyt, "SM", "value", healthy.cols)+
    facet_wrap(~variable, ncol=4, labeller=th_groups)+
    labs(y="(%) Total CD4+ T cells")+coord_cartesian(ylim=c(0,45))+
    labs(title="Healthy Controls")

@@

```{r cytokine, fig.width=15, fig.height=8}
melt<-melt(cyt, id.vars=c("TB","SM", "disease"), measure.vars=c("IFNg", "TNFa"))
a<-baseplot(melt, "SM", "value", ltbi.cols)+    
    facet_wrap(~variable, labeller = cyt_groups)+
    stat_compare_means(method="wilcox.test" , label="p.format", size=4, label.x=1.3, label.y = (.95*.15))+
    coord_cartesian(ylim=c(0,.15))+
    labs(y="(%) CD4+ T cells")

melt<-melt(cyt, id.vars=c("TB","SM", "disease"), measure.vars=c("IL4", "IL13"))
b<-baseplot(melt, "SM", "value", ltbi.cols)+    
    facet_wrap(~variable, labeller = cyt_groups)+
    stat_compare_means(method="wilcox.test" , label="p.format", size=4, label.x=1.3, label.y = (.95*.02))+
    coord_cartesian(ylim=c(0,.02))

@@

tf<-baseplot(melt[melt$variable %in% c("T-bet","GATA3"),], "SM", "value", ltbi.cols)+    
    facet_wrap(~variable)+
    stat_compare_means(method="wilcox.test" , label="p.format", size=4, label.x=1.3, label.y=(.98*70))+
    coord_cartesian(ylim=c(0,70))+
    labs(y="(%) Mtb-Specific TH1 Cytokine+ cells")

sm<-baseplot(melt[melt$variable %in% c("CXCR3", "CCR4"),], "SM", "value", ltbi.cols)+    
    facet_wrap(~variable)+
    stat_compare_means(method="wilcox.test" , label="p.format", size=4, label.x=1.3, label.y=(.98*100))+
    coord_cartesian(ylim=c(0,100))+
    labs(y="(%) Mtb-Specific TH1 Cytokine+ cells")

@@

```{r, fig.width=15, fig.height=8}
melt<-melt(cyt, id.vars=c("TB","SM", "disease"), measure.vars=c("IFNg", "TNFa"))
a<-baseplot(melt, "disease", "value", tb.cols)+    
    facet_wrap(~variable, labeller = cyt_groups)+
    stat_compare_means(method="wilcox.test" , label="p.format", size=4, label.x=1.3, label.y=(.95*.15))+
    coord_cartesian(ylim=c(0,.15))+
    labs(y="(%) CD4+ T cells")

melt<-melt(cyt, id.vars=c("TB","SM", "disease"), measure.vars=c("IL4", "IL13"))
b<-baseplot(melt, "disease", "value", tb.cols)+ 
    facet_wrap(~variable, labeller = cyt_groups)+
    stat_compare_means(method="wilcox.test" , label="p.format", size=4, label.x=1.3, label.y=(.95*.02))+
    coord_cartesian(ylim=c(0,.02))
```

@@

tf<-baseplot(melt[melt$variable %in% c("T-bet","GATA3"),], "SM", "value", tb.cols)+    
    facet_wrap(~variable)+
    stat_compare_means(method="wilcox.test" , label="p.format", size=4, label.x=1.3, label.y=(.98*80))+
    coord_cartesian(ylim=c(0,80))+
    labs(y="(%) Mtb-Specific TH1 Cytokine+ cells")

sm<-baseplot(melt[melt$variable %in% c("CXCR3", "CCR4"),], "SM", "value", tb.cols)+    
    facet_wrap(~variable)+
    stat_compare_means(method="wilcox.test" , label="p.format", size=4, label.x=1.3, label.y=(.98*80))+
    coord_cartesian(ylim=c(0,80))

@@

both<-baseplot(melt, "SM", "value", tb.cols)+    
    facet_wrap(~variable, labeller = groups)+
    stat_compare_means(method="wilcox.test" , label="p.format", size=4, label.x=1.3)+
    labs(y="(%) Mtb-Specific TH1 Cytokine+ cells")

tbcyt<-cowplot::plot_grid(NULL, a, b, nrow=1, labels=c("A","B", "C"), label_size = 20, rel_widths = c(1.5,1,1))
tbphen<-cowplot::plot_grid(tf, sm, both, nrow=1, labels=c("D","E","F"), label_size = 20)
figure5<-cowplot::plot_grid(tbcyt, tbphen, nrow=2, rel_heights = c(2,3))
```

@@

part1<-melt(og, id.vars=c("TB","SM", "disease"), measure.vars="OG")
og<-allplot(part1, "TB", "value", all.cols)+
    facet_wrap(~variable, scales="free", labeller = groups)+
    labs(y="(%) Total CD4+ T cells")

@@

two<-allplot(melt, "TB", "value", all.cols)+    
    facet_wrap(~variable, labeller = groups)
```

@@

first_row = cowplot::plot_grid(NULL, labels = c('A', 'B'), nrow=1, label_size = 20)
second_row = cowplot::plot_grid(og, one, two, nrow=1, rel_widths = c(1.2,2,1), labels=c("B", "C","D"), label_size = 20)
third_row = cowplot::plot_grid(tf, sm, labels=c("E", "F"), nrow=1, label_size = 20)
figure6<-cowplot::plot_grid(first_row, second_row, third_row, nrow=3)
```

@@

tf<-baseplot(melt[melt$variable %in% c("T-bet","GATA3"),], "SM", "value", ltbi.cols)+    
    facet_wrap(~variable)+
    stat_compare_means(method="wilcox.test" , label="p.format", size=4, label.x=1.3, label.y=(.98*100))+
    coord_cartesian(ylim=c(0,100))+
    labs(y="(%) Proliferating Mtb-Specific cells")

sm<-baseplot(melt[melt$variable %in% c("CXCR3", "CCR4"),], "SM", "value", ltbi.cols)+    
    facet_wrap(~variable)+
    stat_compare_means(method="wilcox.test" , label="p.format", size=4, label.x=1.3, label.y=(.98*100))+
    coord_cartesian(ylim=c(0,100))

first_row = cowplot::plot_grid(NULL, labels = c('A'), nrow=1, label_size = 20)
second_row = cowplot::plot_grid(og, one, two, nrow=1, rel_widths = c(1.2,2,1), labels=c("B", "C","D"), label_size = 20)
third_row = cowplot::plot_grid(tf, sm, labels=c("E", "F"), nrow=1, label_size = 20)
figure7<-cowplot::plot_grid(first_row, second_row, third_row, nrow=3)
```

@@

lumplot<-cowplot::plot_grid(a,b, NULL, ncol=1, align = "v", labels=c("A","A", "B"), label_size = 20)
```

@@

pos <- cor(lum[lum$SM=="SM+",3:11], method="spearman")
order.pos <- pos[order, order]
res1 <- cor.mtest(lum[lum$SM=="SM+",3:11], conf.level = .95)
pvals <- res1$p[order, order]
corrplot(order.pos, method = "circle", insig = "label_sig", tl.col = "black", 
         p.mat = pvals, sig.level = c(.001, .01, .05), pch.cex = 2, pch.col = "white",
         type="upper")
```
#Exporting Data
```{r}
setwd("/Users/tarynam/Desktop/Manuscript1")
cowplot::save_plot("figure1.png", figure1, base_height=8, base_width=16) #Figure 1
cowplot::save_plot("figure2.png", figure2, base_height=14, base_width=16) #Figure 2
cowplot::save_plot("figure3.png", figure3, base_height=14, base_width=16)
cowplot::save_plot("figure4.png", figure4, base_height=14, base_width=16)
cowplot::save_plot("figure5.png", figure5, base_height=14, base_width=16)
cowplot::save_plot("figure6.png", figure6, base_height=16, base_width=16)
cowplot::save_plot("figure7.png", figure7, base_height=16, base_width=16)
cowplot::save_plot("figure8.png", lumplot, base_height=32, base_width=16)
```

>>>>

baseplot<-function(data, xval, yval, colors){
    ggplot(data, aes(data[,xval], data[,yval], fill=SM))+
    geom_boxplot(size=1, position=position_dodge(width = 1), outlier.shape = NA)+
    scale_fill_manual(values = colors)+
    theme_classic()+ theme(legend.position="none")+
    theme(panel.border = element_rect(fill = NA, colour = "black"))+
    theme(text = element_text(size=20),
          strip.text = element_text(size = 20))+
    theme(plot.title = element_text(hjust = 0.5)) +
    labs(x="", y="")
}

booleanplot<-function(data, xval, yval, colors){
    ggplot(data, aes(data[,xval], data[,yval], fill=SM))+
    geom_boxplot(size=1, position=position_dodge(width = 1), outlier.shape = NA)+
    scale_fill_manual(values = colors)+
    theme_classic()+ 
    theme(legend.position="none")+
    theme(text = element_text(size=20), 
          axis.text.x = element_text(size=16), 
          strip.text = element_text(size = 20))+
    theme(plot.title = element_text(hjust = 0.5)) +
    stat_compare_means(method="wilcox.test", label="p.signif", hide.ns = TRUE, size=10)+
    labs(x="", y="")
}

allplot<-function(data, xval, yval, colors){
    ggplot(data, aes(data[,xval], data[,yval], fill=disease))+
    geom_boxplot(size=1, position=position_dodge2(width=0.2, padding = 0.2, preserve = "single"), outlier.shape = NA)+
    scale_fill_manual(values = colors)+
    theme_classic()+ 
    theme(legend.position="none") +
    theme(panel.border = element_rect(fill = NA, colour = "black"))+
    facet_wrap(~variable)+
    theme(text = element_text(size=20),
         strip.text = element_text(size = 20))+
    theme(plot.title = element_text(hjust = 0.5))+
    labs(x="", y="")
}

@@

tf<-allplot(melt, "TB", "value", all.cols)+    
    labs(y="(%) Total CD4+ T cells")+
    scale_x_discrete(labels=c("SM- SM+\nHC", "SM- SM+\nLTBI", "SM- SM+\nTB"))+
    stat_compare_means(method = 'wilcox.test', label="p.signif", hide.ns=TRUE, size=10, label.y=25)+
    coord_cartesian(ylim=c(0,30))

@@

sm<-allplot(melt, "TB", "value", all.cols) +    
    scale_x_discrete(labels=c("SM- SM+\nHC", "SM- SM+\nLTBI", "SM- SM+\nTB"))+
    labs(y="(%) Total CD4+ T cells")+
    stat_compare_means(method = 'wilcox.test', label="p.signif", hide.ns=TRUE, size=10, label.y=60)

@@

#Figure 1 alt B

```{r, fig.width=15, fig.height=8}
melt<-melt(cd4, id.vars=c("TB","SM", "disease"), measure.vars=c("T-bet", "GATA3"))

tf<-allplot(melt, "TB", "value", all.cols)+    
    labs(y="(%) Total CD4+ T cells")+
    scale_x_discrete(labels=c("SM- SM+\nHC", "SM- SM+\nLTBI", "SM- SM+\nTB"))+
    stat_compare_means(method = 'wilcox.test', label="p.format", size=6, label.y=.9*30)+
    coord_cartesian(ylim=c(0,30))

sm<-allplot(melt, "TB", "value", all.cols) +    
    labs(y="(%) Total CD4+ T cells")+
    scale_x_discrete(labels=c("SM- SM+\nHC", "SM- SM+\nLTBI", "SM- SM+\nTB"))+
    stat_compare_means(method = 'wilcox.test', label="p.format", size=6, label.y=.9*65)+
    coord_cartesian(ylim=c(0,65))

first_row = cowplot::plot_grid(NULL, NULL, labels = c('A' , 'B'), nrow=1, label_size = 20, rel_widths = c(3,2))
second_row = cowplot::plot_grid(tf, sm,labels = c('C', 'D'), nrow=1, label_size = 20)
figure1B<- cowplot::plot_grid(first_row, second_row, ncol=1, rel_heights = c(1,2))
```

#Figure 1 alt C

```{r, fig.width=15, fig.height=8}
melt<-melt(cd4, id.vars=c("TB","SM", "disease"), measure.vars=c("T-bet", "GATA3"))

tf<-allplot(melt, "disease", "value", all.cols)+    
    labs(y="(%) Total CD4+ T cells")+
    scale_x_discrete(labels=c("HC\nSM-", "HC\nSM+", 
                              "LTBI\nSM-", "LTBI\nSM+", 
                              "TB\nSM-", "TB\nSM+"))+
    stat_compare_means(comparisons=list(c("HC SM-", "HC SM+")), method = 'wilcox.test', label="p.format", size=6, label.y=.9*30)+
    coord_cartesian(ylim=c(0,30))

sm<-allplot(melt, "disease", "value", all.cols) +    
    labs(y="(%) Total CD4+ T cells")+    
    scale_x_discrete(labels=c("HC\nSM-", "HC\nSM+", 
                              "LTBI\nSM-", "LTBI\nSM+", 
                              "TB\nSM-", "TB\nSM+"))+
    stat_compare_means(comparisons=list(c("TB SM-", "TB SM+")),method = 'wilcox.test', label="p.format", size=6, label.y=.9*65)+
    coord_cartesian(ylim=c(0,65))

first_row = cowplot::plot_grid(NULL, NULL, labels = c('A' , 'B'), nrow=1, label_size = 20, rel_widths = c(3,2))
second_row = cowplot::plot_grid(tf, sm,labels = c('C', 'D'), nrow=1, label_size = 20)
figure1C<- cowplot::plot_grid(first_row, second_row, ncol=1, rel_heights = c(1,2))
```

@@

one<-allplot(melt, "TB", "value", all.cols)+ 
    facet_wrap(~variable, labeller = cyt_groups)+
    scale_x_discrete(labels=c("SM- SM+\nHC", "SM- SM+\nLTBI", "SM- SM+\nTB"))+
    labs(y="(%) Total CD4+ T cells")

@@

two<-allplot(melt, "TB", "value", all.cols)+
    facet_wrap(~variable, labeller = cyt_groups)+
    scale_x_discrete(labels=c("SM- SM+\nHC", "SM- SM+\nLTBI", "SM- SM+\nTB"))+
    coord_cartesian(ylim=c(0,8))+
    labs(y="(%) Total CD4+ T cells")

@@

cyt<-filter_hc(melt)
a<-baseplot(cyt, "SM", "value", healthy.cols)+
    facet_wrap(~variable, ncol=4, labeller=th_groups)+
    labs(y="(%) Total CD4+ T cells")+coord_cartesian(ylim=c(0,45))+
    labs(title="HC")

@@

```{r cytokine, fig.width=15, fig.height=8}
melt<-melt(cyt, id.vars=c("TB","SM", "disease"), measure.vars=c("IFNg", "TNFa"))
a<-baseplot(melt, "SM", "value", ltbi.cols)+    
    facet_wrap(~variable, labeller = cyt_groups)+
    stat_compare_means(comparisons=list(c("SM-","SM+")), method="wilcox.test" , label="p.format", size=6, label.x=1.3, label.y = (.90*.15))+
    coord_cartesian(ylim=c(0,.15))+
    labs(y="(%) CD4+ T cells")

melt<-melt(cyt, id.vars=c("TB","SM", "disease"), measure.vars=c("IL4", "IL13"))
b<-baseplot(melt, "SM", "value", ltbi.cols)+    
    facet_wrap(~variable, labeller = cyt_groups)+
    coord_cartesian(ylim=c(0,.02))

@@

tf<-baseplot(melt[melt$variable %in% c("T-bet","GATA3"),], "SM", "value", ltbi.cols)+    
    facet_wrap(~variable)+
    coord_cartesian(ylim=c(0,70))+
    labs(y="(%) Mtb-Specific TH1 Cytokine+ cells")

sm<-baseplot(melt[melt$variable %in% c("CXCR3", "CCR4"),], "SM", "value", ltbi.cols)+    
    facet_wrap(~variable)+
    coord_cartesian(ylim=c(0,100))+
    labs(y="(%) Mtb-Specific TH1 Cytokine+ cells")

@@

```{r, fig.width=15, fig.height=8}
melt<-melt(cyt, id.vars=c("TB","SM", "disease"), measure.vars=c("IFNg", "TNFa"))
a<-baseplot(melt, "SM", "value", tb.cols)+    
    facet_wrap(~variable, labeller = cyt_groups)+
    coord_cartesian(ylim=c(0,.15))+
    labs(y="(%) CD4+ T cells")

melt<-melt(cyt, id.vars=c("TB","SM", "disease"), measure.vars=c("IL4", "IL13"))
b<-baseplot(melt, "disease", "value", tb.cols)+ 
    facet_wrap(~variable, labeller = cyt_groups)+
    coord_cartesian(ylim=c(0,.02))
```

@@

tf<-baseplot(melt[melt$variable %in% c("T-bet","GATA3"),], "SM", "value", tb.cols)+    
    facet_wrap(~variable)+
    stat_compare_means(comparisons=list(c("SM-","SM+")), method="wilcox.test" , label="p.format", size=6, label.x=1.3, label.y=(.98*80))+
    coord_cartesian(ylim=c(0,80))+
    labs(y="(%) Mtb-Specific TH1 Cytokine+ cells")

sm<-baseplot(melt[melt$variable %in% c("CXCR3", "CCR4"),], "SM", "value", tb.cols)+    
    facet_wrap(~variable)+
    coord_cartesian(ylim=c(0,80))

@@

both<-baseplot(melt, "SM", "value", tb.cols)+    
    facet_wrap(~variable, labeller = groups)+
    stat_compare_means(comparisons=list(c("SM-","SM+")), method="wilcox.test" , label="p.format", size=6, label.x=1.3, label.y=.98*13)+
    labs(y="(%) Mtb-Specific TH1 Cytokine+ cells")+
    coord_cartesian(ylim=c(0,13))

tbcyt<-cowplot::plot_grid(NULL, a, b, nrow=1, labels=c("A","B", "C"), label_size = 20, rel_widths = c(1.5,1,1))
tbphen<-cowplot::plot_grid(tf, sm, both, nrow=1, labels=c("D","E","F"), label_size = 20)
figure5<-cowplot::plot_grid(tbcyt, tbphen, nrow=2, rel_heights = c(2,2))
```

@@

part1<-melt(og, id.vars=c("TB","SM", "disease"), measure.vars="OG")
og<-allplot(part1, "TB", "value", all.cols)+
    facet_wrap(~variable, scales="free", labeller = groups)+
    scale_x_discrete(labels=c("SM- SM+\nHC", "SM- SM+\nLTBI", "SM- SM+\nTB"))+
    labs(y="(%) Total CD4+ T cells")

@@

two<-allplot(melt, "TB", "value", all.cols)+    
    facet_wrap(~variable, labeller = groups)+
    scale_x_discrete(labels=c("SM- SM+\nHC", "SM- SM+\nLTBI", "SM- SM+\nTB"))+
    coord_cartesian(ylim=c(0,5))
```

@@

first_row = cowplot::plot_grid(NULL, NULL, labels = c('A', 'B'), nrow=1, label_size = 20, rel_widths = c(3,1))
second_row = cowplot::plot_grid(og, one, two, nrow=1, rel_widths = c(1,2,1), labels=c("C","D","E"), label_size = 20)
third_row= cowplot::plot_grid(tf, sm, labels=c('F', 'G'), nrow=1, label_size = 20)

figure6<-cowplot::plot_grid(first_row, second_row, third_row, nrow=3, rel_heights = c(1.5,2,2))
```

@@

tf<-baseplot(melt[melt$variable %in% c("T-bet","GATA3"),], "SM", "value", ltbi.cols)+    
    facet_wrap(~variable)+
    coord_cartesian(ylim=c(0,100))+
    labs(y="(%) Proliferating Mtb-Specific cells")

sm<-baseplot(melt[melt$variable %in% c("CXCR3", "CCR4"),], "SM", "value", ltbi.cols)+    
    facet_wrap(~variable)+
    coord_cartesian(ylim=c(0,100))

first_row = cowplot::plot_grid(NULL, labels = c('A'), nrow=1, label_size = 20)
second_row = cowplot::plot_grid(og, one, two, nrow=1, rel_widths = c(1.2,2,1), labels=c("B", "C","D"), label_size = 20)
third_row = cowplot::plot_grid(tf, sm, labels=c('E', 'F'), nrow=1, label_size = 20)
figure7<-cowplot::plot_grid(first_row, second_row, third_row, nrow=3, rel_heights = c(2,2,2))
```

@@

c<-baseplot(melt, "SM", "value", ltbi.cols)+facet_wrap(~variable, scales="free")+
    labs(y="pg/mL")+
    coord_cartesian(ylim=c(0,20))

lumplot<-cowplot::plot_grid(a,b,c, NULL, ncol=1, align = "v", labels=c("A","A", "A", "B"), label_size = 20)
```

@@

pos <- cor(lum[lum$SM=="SM+",3:11], method="spearman")
order.pos <- pos[order, order]
res1 <- cor.mtest(lum[lum$SM=="SM+",3:11], conf.level = .95)
pvals <- res1$p[order, order]
corrplot(order.pos, method = "circle", insig = "label_sig", tl.col = "black", 
         p.mat = pvals, sig.level = c(.001, .01, .05), pch.cex = 2, pch.col = "white",
         type="upper")
```
#Exporting Data
```{r}
setwd("/Users/tarynam/Desktop/Manuscript1")

cowplot::save_plot("figure1.png", figure1, base_height=8, base_width=16) #Figure 1
cowplot::save_plot("figure1alt1.png", figure1B, base_height=8, base_width=16) #Figure 1
cowplot::save_plot("figure1alt2.png", figure1C, base_height=8, base_width=16) #Figure 1
cowplot::save_plot("figure2.png", figure2, base_height=14, base_width=16) #Figure 2
cowplot::save_plot("figure3.png", figure3, base_height=14, base_width=16)
cowplot::save_plot("figure4.png", figure4, base_height=14, base_width=12)
cowplot::save_plot("figure5.png", figure5, base_height=14, base_width=16)
cowplot::save_plot("figure6.png", figure6, base_height=16, base_width=16)
cowplot::save_plot("figure7.png", figure7, base_height=16, base_width=16)
cowplot::save_plot("figure8.png", lumplot, base_height=48, base_width=16)
```
